---
title: "Project AB test - Guillem Bonilla"
output: html_notebook
---

```{r}
library('data.table')
library("ggplot2")
library("pwr")
library(tidyverse)
```
## Exploratory Analysis

```{r}
df <- fread("views_leads_pre.csv")[date > '2019-03-24',]
```

### Metrics

* Convertion Rate
* Number of page views per user
* Number of leads per user
* Daily Active Users (DAU)
* Second Day Return Rate (*)


#### Convertion Rate

```{r}
cr <- sum(df[, numLeads])/sum(df[, numViews])
cr
```

#### Daily Convertion Rate

```{r}
cr_daily_df <-  df[, .(numLeads = sum(numLeads), numViews=sum(numViews)), by=date]
cr_daily_df[, cr := numLeads/numViews]
ggplot(data=cr_daily_df, aes(x=date, y=cr, group=1)) +
  geom_line() +
  geom_point() +
  geom_hline(yintercept=cr, linetype="dashed", color = "red") +
  labs(x = "Date", y = "Conversion Rate", 
       title = "Daily Conversion Rate", 
       subtitle = paste("Total Conv. Rate = ", round(100*cr,2),"%")) +
  theme_light()
```

#### Number of active users

```{r}
users <- length(df[, unique(cookie)])
users
```


```{r}
users_daily_df <- df[, .(users=length(unique(cookie))), by=date]
users_daily_df
```

```{r}
ggplot(data=users_daily_df, aes(x=date, y=users, group=1)) +
  geom_line() +
  geom_point() +
  theme_light()
```

#### Number of page views per user

```{r}
sum(df[, numViews])/users
```

#### Unique users report

* Number of page view per user 
* Number of leads per user
* Conversion rate per user

```{r}
(users = df %>% distinct(cookie, .keep_all = TRUE) %>% select(date, numLeads, numViews) %>% 
  mutate(ConvRate = ifelse(numViews>0, numLeads/numViews, 0)))
```

```{r}
# Number of page view per user -- another way to compute it
mean(users$numViews)

# Number of leads per user
mean(users$numLeads)

# Conversion rate per user
mean(users$ConvRate)
```

#### Daily report

Daily report of views, leads and conversion rate

```{r}
(daily = df %>% distinct(cookie, .keep_all = TRUE) %>% 
   select(date, numLeads, numViews) %>% 
   mutate(ConvRate = ifelse(numViews>0, numLeads/numViews, 0)) %>%
   group_by(date) %>%
   summarise(Leads = sum(numLeads), Views = sum(numViews), CR = mean(ConvRate)))
```


#### Daily Active Users (DAU)

```{r}
(DAU = df %>% filter(numViews > 0 | numLeads > 0) %>%
  distinct(cookie, .keep_all = TRUE) %>%
  group_by(date) %>% summarise(DAU = length(cookie)))
```

```{r}
ggplot(data=DAU, aes(x=date, y=DAU, group=1)) +
  geom_line() +
  geom_point() +
  geom_hline(yintercept = mean(DAU$DAU), linetype = "dashed", color = "red") +
  labs(x = "Date", y = "Active Users", 
       title = "Daily Active Users (DAU)", 
       subtitle = paste("DAU = ", round(mean(DAU$DAU),2))) +
  theme_light()
```

### Sample size determination

```{r}
p <- cr 
s <- sqrt(p*(1-p))
improve_by <- 0.05
diff <- cr * improve_by
diff # This is the true differences between the means

power.t.test(delta = diff, sd = s, sig.level = 0.05, power = 0.8, type = "two.sample")
```

```{r}
# An alternative way to run the test
pwr.t.test(d=diff/s, sig.level = 0.05, power=0.8)
```

```{r}
cr_daily_df[, .(date, numViews)]
```

We need at least 2 days


## AB Test Analysis

```{r}
df_ab <- fread("views_leads_ab.csv")[date >= '2019-04-07' & date <= '2019-04-13',]
df_ab
```

The AB Test was running from 2019-04-07 through 2019-04-13. We have selected the coresponging rows of data.

```{r}
############################################
### FUNCTIONS TO COMPUTE POOLED P-VALUES ###
############################################

p_value = function(z_score, side = 1){
  
  # side = 0: if null hypotesis successes_control == successes_treatment (P-VALUE)
  # side = 1: if null hypothesis successes_control >= successes_treatment (POWER)
  # side = -1: if null hypothesis successes_control <= successes_treatment
  
  cum_dist = pnorm(z_score)
  if (side == 1)
    return(1 - cum_dist)
  else if (side == -1)
    return(cum_dist)
  else
    return(2*min(1 - cum_dist, cum_dist))
}


pooled_two_proportions_zscore = function(size_control, size_treatment, successes_control, successes_treatment){
  p_control = successes_control/size_control
  p_treatment = successes_treatment/size_treatment
  p_pooled = (successes_control + successes_treatment) / (size_control + size_treatment)
  sd_pooled = sqrt(p_pooled * (1-p_pooled))
  se_pooled = sd_pooled * sqrt(1/size_control + 1/size_treatment)
  z_score = (p_treatment - p_control) / se_pooled
  return(z_score)
}

get_p_value = function(size_control, size_treatment, successes_control, successes_treatment, side=0){
  z_score = pooled_two_proportions_zscore(size_control, size_treatment, successes_control, successes_treatment)
  return(p_value(z_score, side))
}
```


#### Size of unique users per variant

```{r}
df_ab %>% distinct(cookie, .keep_all = TRUE) %>% select(variant) %>% 
  group_by(variant) %>%
  summarise(Size = length(variant))
```


#### Number of views by variant

```{r}
Views = df_ab %>% distinct(cookie, .keep_all = TRUE) %>% select(variant, numViews) %>% 
  group_by(variant) %>% summarise(Views = sum(numViews))
Views
```


#### Number of leads by variant

```{r}
Leads = df_ab %>% distinct(cookie, .keep_all = TRUE) %>% select(variant, numLeads) %>% 
  group_by(variant) %>% summarise(Leads = sum(numLeads))
Leads
```

#### Conversion Rate by variant

```{r}
df_ab %>% distinct(cookie, .keep_all = TRUE) %>% select(variant, numLeads, numViews) %>% 
  mutate(ConvRate = ifelse(numViews>0, numLeads/numViews, 0)) %>%
  group_by(variant) %>% 
  summarise(CR = mean(ConvRate))
```

#### Daily number of Leads by Variant

```{r}
(DL = df_ab %>% 
  distinct(cookie, .keep_all = TRUE) %>% 
  select(date,numLeads,variant) %>%
  group_by(date, variant) %>% 
  summarise(Leads = sum(numLeads)))
```

```{r}
ggplot(DL, aes(x=date, y=Leads, group=variant)) +
  geom_line(aes(linetype=variant, color=variant))+
  geom_point(aes(color=variant))+
  theme_light()
```


### Hypothesis testing

As null hypothesis successes_control <= successes_treatment, then:
$$
side=-1
$$ 

```{r}
get_p_value(size_control = as.numeric(Views[Views$variant == "A",2]), 
            size_treatment =  as.numeric(Views[Views$variant == "B",2]), 
            successes_control = as.numeric(Leads[Leads$variant == "A",2]), 
            successes_treatment = as.numeric(Leads[Leads$variant == "B",2]), 
            side = -1)
```

As the p-value is lower than the level of significance $\alpha = 0.05$, then the null hypothesis, which states that `successes_control <= successes_treatment` is rejected. Therefore, we can conclude that we have enough evidence to say that the treatment group does not have a statistically significant higher successes numbers. 

Moreover, the AB test has shown us that adding buyer's ratings to a product page has not increase the leads in a statistically significant way. 






